---
title: "Stryker Comparison Plots"
output: html_document
date: "2024-07-26"
---

```{r}
rootdir="./"
outdir="plots/"
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source(paste0(rootdir,"stryker_header.r"), chdir=TRUE)

library(scales)
```

```{r cars}
get_data = function(filename,srcname,readcols=c("variable","q025","mean","q975")) {
  dfin = read.csv(filename)
  dfout = dfin[,readcols]
  colnames(dfout) = c("Variant","mmbsa95lower","mmbsa","mmbsa95upper")
  dfout$Method = srcname
  return (dfout)
}

compare_ot_ref = get_data("results/otonly/refpr/mmbsa_stats.csv"      ,"(1) OT (Weakly Informative)")
compare_dw_ref = get_data("results/dw/refpr/mmbsa_stats.csv"       ,"(2) DT/OT - Downweight (Weakly Informative)")
compare_dw     = get_data("results/dw/infpr/mmbsa_stats.csv"       ,"(3) DT/OT - Downweight (Informative)")
compare_npp    = get_data("results/npp/infpr/mmbsa_stats.csv"         ,"(4) DT/OT - NPP (Informative)")
```

# Compare Methods

Compare methods:
```{r pressure, echo=FALSE}
compareDf = rbind(compare_ot_ref,compare_dw_ref,compare_dw,compare_npp)
pd = position_dodge(0.5)
ggplot(data=compareDf, aes(x=Variant, y=mmbsa, color=Method)) +
  geom_point(position=pd) + geom_errorbar(aes(ymin=mmbsa95lower,ymax=mmbsa95upper),width=0.2,position=pd) +
  geom_hline(yintercept=1000, linetype="dashed") +
  ylab('Mean Miles Before System Abort') + xlab('Vehicle Variant') + coord_cartesian(ylim=c(0,10000)) + # ylim(0,10000) + 
  theme(legend.position="bottom",aspect.ratio=0.5) +
  guides(color = guide_legend(nrow = 2))
ggsave(paste0(outdir,"compare_methods.png"))
ggsave(paste0(outdir,"compare_methods.pdf"))
```

# Parameter Inference
```{r}
variantNames = unique(compareDf$Variant)

dirDf = data.frame(Directory = character(),Method = character(), stringsAsFactors = FALSE)
dirDf[1,] = c("results/otonly/refpr" ,"(1) OT (Weakly Informative)")
dirDf[2,] = c("results/dw/refpr"  ,"(2) DT/OT - Downweight (Weakly Informative)")
dirDf[3,] = c("results/dw/infpr"  ,"(3) DT/OT - Downweight (Informative)")
dirDf[4,] = c("results/npp/infpr"    ,"(4) DT/OT - NPP (Informative)")

extractRData <- function(file, object) {
  E <- new.env()
  load(file=file, envir=E)
  return(get(object, envir=E, inherits=F))
}

extractPosteriorSamples <- function(dirDf) {
  outDf = data.frame(Method = character(), beta = numeric(), eta.1 = numeric(), eta.2 = numeric(), eta.3 = numeric(), eta.4 = numeric(), eta.5 = numeric(), eta.6 = numeric(), eta.7 = numeric(), eta.8 = numeric(), stringsAsFactors = FALSE)
  for (i in 1:nrow(dirDf)) {
    tmpDf = tryCatch({
      as.data.frame(extractRData(paste0(dirDf[i,"Directory"],"/data.Rdata"),"mcmc.post"))
    },error = function(e) {
      as.data.frame(extractRData(paste0(dirDf[i,"Directory"],"/data.Rdata"),"mcmc.ot"))
    })
    tmpDf$Method = dirDf[i,"Method"]
    tmpDf = tmpDf[,colnames(outDf)]
    outDf = rbind(outDf,tmpDf)
  }
  return(outDf)
}
postSamples = extractPosteriorSamples(dirDf)


#beta histogram
ggplot(postSamples) +
  geom_density(aes(x = beta, y = after_stat(density), color=Method), alpha = 0.2) +
  xlab("Shape Parameter") + ylab('Density') +
  theme(legend.position="bottom",aspect.ratio=0.5) +
  guides(color = guide_legend(nrow = 2))
ggsave(paste0(outdir,"beta_hist.png"))
ggsave(paste0(outdir,"beta_hist.pdf"))

#eta plot
etaSamples = dplyr::select(postSamples,contains("eta."))
colnames(etaSamples) = variantNames
etaSamples$Method = postSamples$Method
etaStats = melt(etaSamples,id.vars="Method",variable.name = "Variant") %>% group_by(Method,Variant) %>%
  summarize(
    q025 = quantile(value,0.025), 
    median=median(value),
    mean=mean(value),
    q975 = quantile(value,0.975)
  )

pd = position_dodge(0.5)
p = ggplot(data=etaStats, aes(x=Variant, y=median, color=Method)) +
  geom_point(position=pd) + geom_errorbar(aes(ymin=q025,ymax=q975),width=0.2,position=pd) +
  #geom_hline(yintercept=1000, linetype="dashed") +
  ylab('Scale Parameter') + xlab('Vehicle Variant') + #coord_cartesian(ylim=c(0,10000)) + # ylim(0,10000) +
  theme(legend.position="bottom",aspect.ratio=0.5) +
  guides(color = guide_legend(nrow = 2))
print(p)
ggsave(paste0(outdir,"eta_yall.png"))
ggsave(paste0(outdir,"eta_yall.pdf"))

p = p + coord_cartesian(ylim=c(0,10000))
print(p)ggsave(paste0(outdir,"eta.png"))
ggsave(paste0(outdir,"eta.pdf"))

```
# Results by Method

```{r}
out_prefix = gsub("/","_",gsub("results/","",dirDf$Directory))
meth_outdir = paste0(outdir,"by_method/")
dir.create(meth_outdir, showWarnings = FALSE)
threshold = 1000

mmbsa_gt_thresh_df = data.frame(Variant=character(),Method=character(),p_thresh=double())

for (i in 1:length(unique(postSamples$Method))) {
  method = unique(postSamples$Method)[i]
  methSamples = postSamples[postSamples$Method == method,]
  #methSamples = postSamples[postSamples$Method == unique(postSamples$Method)[i],]
  
  #library(presenter)
  melt(methSamples,id.vars = 'Method') %>%
    group_by(variable) %>%
    summarize(
      mean=mean(value), #sd=sd(value), 
      median=median(value), #min=min(value), 
      q025 = quantile(value,0.025, na.rm = TRUE), 
      q05  = quantile(value,0.05, na.rm = TRUE), 
      q10  = quantile(value,0.1, na.rm = TRUE), 
      q25  = quantile(value,0.25, na.rm = TRUE), 
      q75  = quantile(value,0.75, na.rm = TRUE), 
      q90  = quantile(value,0.9, na.rm = TRUE), 
      q95  = quantile(value,0.95, na.rm = TRUE), 
      q975 = quantile(value,0.975, na.rm = TRUE), #max=max(value),
      p_thresh = mean(value > threshold, na.rm = TRUE)
    ) %>% #pivot_summary(variable) %>%
    write.table(file=paste0(meth_outdir,out_prefix[i],".csv"),sep=",",row.names=FALSE)
  
  #shape
  plot1 = ggplot(methSamples) + geom_density(aes(x = beta, y = after_stat(density))) + xlab("Shape Parameter") + ylab('Density')
  ggsave(paste0(meth_outdir,out_prefix[i],"_beta_hist.png"), dpi = 300, width=3, height=3)
  ggsave(paste0(meth_outdir,out_prefix[i],"_beta_hist.pdf"), dpi = 300, width=3, height=3)
  
  #scale
  etaSamples = dplyr::select(methSamples,contains("eta."))
  colnames(etaSamples) = variantNames
  methEta = melt(etaSamples,variable.name = "Variant")
  methEta = methEta[methEta$Variant == c("CV","FSV","MC","MEV","RV"),]
  plot2 = ggplot(methEta) +
    geom_density(aes(x = value, y = after_stat(density), color=Variant), alpha = 0.2) +
    xlab("Scale Parameter") + ylab('Density') + xlim(0,10000) #+ theme(legend.position="bottom",aspect.ratio=0.5) + guides(color = guide_legend(nrow = 2))
  
  #mmbsa
  methMmbsa = as.data.frame( weibullMean(as.vector(methSamples$beta),as.matrix(etaSamples)) )
  methMmbsa = melt(methMmbsa,id.vars = NULL,variable.name = "Variant")

  #assemble prob(mmbsa > threshold) so we can compare across methods/variants
  methMmbsa$Method=method
  mmbsa_gt_thresh_df = rbind(mmbsa_gt_thresh_df,methMmbsa %>% group_by(Method,Variant) %>% summarize(p_thresh = mean(value > threshold, na.rm = TRUE),p_thresh2 = mean(value > 2*threshold, na.rm = TRUE)) %>% as.data.frame())

  #now plot
  methMmbsa = methMmbsa[methMmbsa$Variant == c("CV","FSV","MC","MEV","RV"),]
  plot3 = ggplot(methMmbsa) + geom_density(aes(x = value, y = after_stat(density), color=Variant), alpha = 0.2) +
    xlab("MMBSA") + ylab('Density') + xlim(0,10000) #+ theme(legend.position="bottom",aspect.ratio=0.5) + guides(color = guide_legend(nrow = 2))
  
  plot_out = ggpubr::ggarrange(plot2,plot3, nrow=1, common.legend = TRUE)
  ggsave(paste0(meth_outdir,out_prefix[i],"_eta_mmbsa_hist.png"), dpi = 300, width=6, height=3)
  ggsave(paste0(meth_outdir,out_prefix[i],"_eta_mmbsa_hist.pdf"), dpi = 300, width=6, height=3)
  plot_out = ggpubr::ggarrange(plot1,plot2,plot3, nrow=1, common.legend = TRUE, widths=c(1,1.25,1.25))
  ggsave(paste0(meth_outdir,out_prefix[i],"_hist.png"), dpi = 300, width=8, height=3)
  ggsave(paste0(meth_outdir,out_prefix[i],"_hist.pdf"), dpi = 300, width=8, height=3)
}
```

# Probability > thresh
```{r}
ggplot(data=mmbsa_gt_thresh_df, aes(x=Variant, y=p_thresh, fill=Method)) +
  geom_bar(stat="identity",position=position_dodge()) + ylab('Probability of MMBSA > 1,000') + xlab('Vehicle Variant') +
  theme(legend.position="bottom",aspect.ratio=0.5) + guides(fill = guide_legend(nrow = 2))
ggsave(paste0(outdir,"compare_p_thresh.png"))
ggsave(paste0(outdir,"compare_p_thresh.pdf"))

ggplot(data=mmbsa_gt_thresh_df, aes(x=Variant, y=p_thresh2, fill=Method)) +
  geom_bar(stat="identity",position=position_dodge()) + ylab('Probability of MMBSA > 2,000') + xlab('Vehicle Variant') +
  theme(legend.position="bottom",aspect.ratio=0.5) + guides(fill = guide_legend(nrow = 2))
ggsave(paste0(outdir,"compare_p_thresh2.png"))
ggsave(paste0(outdir,"compare_p_thresh2.pdf"))
```

# Raw Data

```{r}
df = extractRData(paste0(dirDf$Directory[1],"/data.Rdata"),"df")
df$rightCensor = as.factor(df$rightCensor)

ggplot(df,aes(VehicleVariant,MBSA)) + geom_boxplot()
ggplot(df,aes(VehicleVariant,MBSA)) + geom_boxplot(aes(color=TestPhase))
ggplot(df,aes(VehicleVariant,MBSA)) + geom_boxplot(aes(color=as.factor(ExactFailure)))
ggplot(df,aes(VehicleVariant,MBSA)) + geom_boxplot(aes(color=TestPhase,linetype=rightCensor)) + 
  labs(x="Vehicle Variant",y="Miles Before System Abort",color="Test Phase",linetype="Right Censor") +
  theme(legend.position="bottom",aspect.ratio=0.5) + ylim(0,10000)
ggsave(paste0(outdir,"dataset_whisker.png"))
ggsave(paste0(outdir,"dataset_whisker.pdf"))
```

```{r}
ggplot(df[df$VehicleVariant=="CV",]) + geom_freqpoly(aes(x=MBSA,color=TestPhase,linetype=rightCensor),linewidth=1) + 
  labs(x="Miles Before System Abort",y="Count",color="Test Phase",linetype="Right Censor",title="Raw Data for CV Variant") +
  theme(legend.position="bottom",aspect.ratio=0.5)

df[df$VehicleVariant=="CV",] %>% group_by(TestPhase,rightCensor) %>% summarise(Count=n(),MMBSA=mean(MBSA),Median=median(MBSA))

ggsave(paste0(outdir,"cv_freqpoly.png"))
ggsave(paste0(outdir,"cv_freqpoly.pdf"))

df$PhaseAndType = paste(df$TestPhase,"/",ifelse(df$ExactFailure==0,"Right Censor","Exact Failure"))
ggplot(df[df$VehicleVariant=="CV",]) + 
  geom_histogram(aes(x=MBSA),color="black",alpha=0.8,position = 'identity') + 
  labs(x="Miles Before System Abort",y="Count") +
  facet_wrap(~PhaseAndType) + 
  theme(legend.position="bottom",aspect.ratio=0.5,strip.background=element_rect(fill="white"))
ggsave(paste0(outdir,"cv_4hist.png"), dpi = 300, width=7, height=4)
ggsave(paste0(outdir,"cv_4hist.pdf"), dpi = 300, width=7, height=4)

ggplot(df[df$VehicleVariant=="CV",]) + 
  geom_histogram(aes(x=MBSA,fill=rightCensor),alpha=0.5,position = 'identity') + 
  labs(x="Miles Before System Abort",y="Count",fill="Right Censor") +
  facet_wrap(~TestPhase) + 
  theme(legend.position="bottom",aspect.ratio=0.5,strip.background=element_rect(fill="white")) +
  guides(fill = guide_legend(override.aes = list(size = 0)))
ggsave(paste0(outdir,"cv_2hist.png"), dpi = 300, width=7, height=3)
ggsave(paste0(outdir,"cv_2hist.pdf"), dpi = 300, width=7, height=3)```
```



```{r pressure, echo=FALSE}
# varCntDf = df[df$ExactFailure==1,] %>% 
varCntDf = df %>% 
  group_by(VehicleVariant) %>% 
  summarise(count=n(),miles=sum(MilesBeforeSystemAbort))

# ggplot(data=varCntDf) +
#   geom_point(aes(x=VehicleVariant, y=count)) +
#   ylab('System Aborts') + xlab('Vehicle Variant')

coeff = 1/1000
#pltColors <- hue_pal()(2)#[c(1,3)]
pltColors = c("black","red")
ggplot(data=varCntDf) +
  geom_point(aes(x=VehicleVariant, y=miles),color=pltColors[1]) +
  geom_point(aes(x=VehicleVariant, y=count/coeff),color=pltColors[2]) +
  xlab('Vehicle Variant')  +
  scale_y_continuous(
    limits = c(0,NA),
    # Features of the first axis
    name = "Miles",
    # Add a second axis and specify its features
    sec.axis = sec_axis(~.*coeff, name="System Aborts")
  ) + 
  #theme_ipsum() +
  theme(
    axis.title.y       = element_text(color = pltColors[1],angle=90),
    #axis.text.y        = element_text(color = pltColors[1]),
    axis.title.y.right = element_text(color = pltColors[2]),
    #axis.text.y.right  = element_text(color = pltColors[2])
  )

ggsave(paste0(outdir,"miles_aborts.png"))
ggsave(paste0(outdir,"miles_aborts.pdf"))
```

# Sensitivity
```{r}
sens_df = read.csv("../../sensitivity/paper2/mmbsa_stats_infpr_ot.csv")

## paper2 stuff ###
sens_df['beta.std'] = sens_df$beta.mean * sens_df$beta.ratio
sens_df[ 'eta.std'] = sens_df$eta.mean  * sens_df$eta.ratio

#count number of changes from base assumptions
sens_df['deviations'] = (sens_df$eta.mean!=1075)+(sens_df$eta.ratio!=0.5)+(sens_df$beta.mean!=1.0)+(sens_df$beta.ratio!=0.5)+(sens_df$dw.factor!=1.5)

#factors
factors = c("beta.mean","beta.ratio","eta.mean","eta.ratio","dw.factor")
factorLabels = c("Shape Mean","Shape Std/Mean","Scale Mean","Scale Std/Mean","Downweight Factor")
```

## One Change from Base Assumptions
```{r}
dev1_df = sens_df[sens_df$deviations<=1,]
dev1_df[order(-dev1_df$mean_CV),c(factors,"mean_CV","deviations")]
```

```{r}
#pull out the means for each variant and some prefix columns (factors + deviations)
statCol="mean"
sens_stat_df = sens_df[,names(sens_df) %in% factors | names(sens_df)=="deviations" | grepl(paste0(statCol,"_"), names(sens_df))]
#stack them so variants are in separate rows
sens_stat_df = sens_stat_df %>% pivot_longer(cols=starts_with(statCol),names_to="variant",names_prefix=paste0(statCol,"_"),values_to = "mean")
sens_stat_df
```

```{r}
factor_plots = lapply(seq(5), function(i){
  plotFactor = factors[i]
  plotLabel  = factorLabels[i]
  tmp_df = sens_stat_df %>% group_by(!!sym(plotFactor),variant) %>% summarize(MMBSA = mean(!!sym(statCol)))

  ggplot(data=tmp_df,aes(x=!!sym(plotFactor),y=MMBSA,color=variant)) + geom_line() + geom_point() + xlab(plotLabel)
  }
)
factor_p = ggpubr::ggarrange(plotlist=factor_plots, nrow=3, ncol=2, common.legend = TRUE)
ggsave(paste0(outdir,"sensitivity.png"), factor_p, dpi = 300, width=6, height=9)
ggsave(paste0(outdir,"sensitivity.pdf"), factor_p, dpi = 300, width=6, height=9)
```

```{r}
factorGrid = data.frame(factor1=c(3,3,4), factor2=c(4,5,5))
factorGrid = merge(factorGrid,data.frame(variant=c("ATGMV","CV","MC")))

#get ranges for all pairwise combinations so we can make plots with a common scale
factorGrid[,c("min_val","max_val")] = t(apply(factorGrid,1, function(rw){
  #filter by variant
  tmp_df = sens_stat_df[sens_stat_df$variant==rw[3],]

  plotFactor1 = factors[as.integer(rw[1])]
  plotFactor2 = factors[as.integer(rw[2])]
  tmp_df = tmp_df %>% group_by(!!sym(plotFactor1),!!sym(plotFactor2),variant) %>% summarize(MMBSA = mean(!!sym(statCol)))
  #return(list(min_val=min(tmp_df$MMBSA),max_val=max(tmp_df$MMBSA)))
  c(min(tmp_df$MMBSA),max(tmp_df$MMBSA))
  }
))

plot_ranges = factorGrid %>% group_by(variant) %>% summarize(min_val=min(min_val),max_val=max(max_val))
factorGrid = merge(subset(factorGrid,select=-c(min_val,max_val)),plot_ranges,by="variant",all.x=TRUE)

#for all pairwise combinations
twofactor_plots = apply(factorGrid,1, function(rw){
  variant = rw[1]
  idx1 = as.integer(rw[2])
  idx2 = as.integer(rw[3])
  min_val = floor(as.numeric(rw[4])/10)*10
  max_val = ceiling(as.numeric(rw[5])/10)*10

  #filter by variant
  tmp_df = sens_stat_df[sens_stat_df$variant==variant,]

  med_val = round(as.numeric(tmp_df[tmp_df$deviations==0,statCol]))

  plotFactor1 = factors[idx1]
  plotFactor2 = factors[idx2]
  plotLabel1  = factorLabels[idx1]
  plotLabel2  = factorLabels[idx2]
  tmp_df = tmp_df %>% group_by(!!sym(plotFactor1),!!sym(plotFactor2),variant) %>% summarize(MMBSA = mean(!!sym(statCol)))

  ggplot(data=tmp_df,aes(x=as.factor(!!sym(plotFactor1)),y=as.factor(!!sym(plotFactor2)),fill=MMBSA)) + geom_tile() + labs(x=plotLabel1,y=plotLabel2) +#,fill=paste("MMBSA,",variant,"Variant")) + 
    scale_fill_continuous(type="viridis",limits = c(min_val,max_val),breaks = c(min_val,med_val,max_val))
  }
)
for (variant in unique(factorGrid$variant)) {
  twofactor_p = ggpubr::ggarrange(plotlist=twofactor_plots[factorGrid$variant==variant], nrow=1, common.legend = TRUE)
  twofactor_p = ggpubr::annotate_figure(twofactor_p, top=ggpubr::text_grob(paste(variant,"Variant"),color="black",face="bold"))#, size=14))
  ggsave(paste0(outdir,"sens_interact_",variant,".png"), twofactor_p, dpi = 300, width=8, height=3)
}
```