---
title: "Analysis of Stryker Dataset via OT data Only"
output:
  html_notebook: default
  html_document:
    df_print: paged
  word_document: default
---
This is an R notebook to estimate the reliability of the Stryker family of vehicles. This version builds priors on the parameters of a Weibull distribution and then conducts Bayesian inference to update those parameters using data from Operational Testing (OT).


# Setup
```{r}
pr.type = "refpr"
#pr.type = "infpr"
rootdir="./"
outdir=paste0("results/otonly/",pr.type,"/")
```
Here, we load in the libraries necessary for our analysis.
```{r}
source(paste0(rootdir,"stryker_header.r"), chdir=TRUE)
```

# Read Data
These lines read the data into the R environment and print the first few rows.
```{r}
df = strykerData(paste0(rootdir,"data/stryker.csv"))
variantNames = sort(unique(df$VehicleVariant))
nVariants = length(variantNames)
head(df)
```


# Split the data
Finally, we split the data into the DT and OT phases.
```{r}
dtDf = df[df$TestPhase == "DT",]
otDf = df[df$TestPhase == "OT",]
```


# Build the Prior #

We're going to use gamma distributions as the priors for the $\beta$ and $\eta$ parameters. These parameters will have much different scales, so here we'll compute the gamma distributions that have the mean and standard deviation that we think is appropriate for those parameters.

```{r}
# pr.params = priorParameters(beta.mean.pr=1, beta.std.pr=2,
#                          eta.mean.pr=1000, eta.std.pr=2000)
# pr.params = priorParameters(beta.mean.pr=1, beta.std.pr=0.3,
#                          eta.mean.pr=1020, eta.std.pr=500)
# outdir = paste0(outdir,"infpr/")
# pr.params = list(betashape=0.001, betarate=0.001, etashape=1e-6, etarate=1e-6)
# outdir = paste0(outdir,"refpr/")
source(paste0("priors/",pr.type,".r"))
```


Here we compute the MMBSA implied by the priors that we have chosen.
```{r}
mmbsa.prior.stats = impliedMmbsaStats(100000,pr.params,variantNames)
print(mmbsa.prior.stats)
write.table(mmbsa.prior.stats,file=paste0(outdir,"mmbsa_stats_prior.csv"),sep=",",row.names=FALSE)
```

# Compute Posterior
```{r}
mcmc.ot = computeWeibullPosterior(otDf,nVariants,pr.params,paste0(rootdir,"stan/weibull_gamma_gamma.stan"))
```

```{r}
mcmc.stats.ot  = summaryStats(mcmc.ot)
mmbsa.ot.stats = mmbsaSummaryStats(mcmc.ot$beta,mcmc.ot$eta,variantNames)
print(mmbsa.ot.stats)
#save mmbsa stats
write.table(mmbsa.ot.stats,file=paste0(outdir,"mmbsa_stats.csv"),sep=",",row.names=FALSE)

save.image(file=paste0(outdir,"data.Rdata"))
```
